\documentclass[openany,oneside,12pt,hidelinks]{book}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{marginnote}
\usepackage{parskip}
  \usepackage{tikz} 
  \usetikzlibrary{calc,arrows.meta,decorations.pathreplacing}
\usepackage{setspace}
\usepackage{csquotes}
\usepackage{caption}
%Document Organisation: 
\author{Zain Sikand}
\title{Problem Catalogue}
\geometry{a4paper,portrait, margin=2cm}
\date{Winter 2025}
%Starting Document:  
\begin{document}
\begin{raggedright}
    %Formatting: 
    \pagenumbering{arabic}
    \maketitle
    \tableofcontents
    \newpage
    %Introduction: 
    \section{Introduction:}
    A collection of hellish maths and physics problems, lacking boundarie and pushing the will of an A-Level student. These problems break down their understanding of maths and physics fundamentally. No form of revision or study at their age aids in the misery bestowed upon them via these problems. 
    %Section 1: 
    \chapter{Mathematics}
    \textit{\emph{Definition:} Mathematics,} \textbf{The foundational means to which we, as a lost species amongst the cosmos, attempt to rationalise our existence, attempt to control reality, and attempt to legitimise our purpose as a species.}

    \newpage
    \section{Integrals}
    \subsection{\underline{Problem One:}} \par

    \textbf{\emph{Problem Author: Zain Sikand}} \\
    \textit{Your final answer should be a single expression in the form $I_1=[h(x)]_{a}^{b}$ where b and a are bounds of $I_1$ to be found}
    \newline \\
    Conclude whether or not the below integral, $I_1:$
    $$I_{1}= \int_{\int_{x}^{2x}(\ln x)^{2}}^{(3+x)^{6}}(\frac{1}{3e^{x}\cos x \sec^{2} x} + \cot x \csc x) \ dx $$
    can be written as a single expression, with all integration expressions evaluated.
    \newline \\
    {Your conclusion must be supported, \textbf{either}, by an attempt to evaluate the integral or, a proof that  $I_{1}$ has no real anti-derivative.}
    \newline \\
    \textit{[6 Marks]} \\
    \newpage
    \subsubsection{Worked Solution:}
    $$I_{1} = \int_{\int_{x}^{2x}(lnx)^{2}}^{(3+x)^{6}}(\frac{1}{3e^{x}\cos x \sec^{2} x} + \cot x \csc x) \ dx $$
    $\Rightarrow \ I_{1}=\int_{b}^{a} f(x) dx$ \\

    $\therefore \ let \ I_{2}=b$ \\
    $$I_2=\int_{x}^{2x}(\ln|x|)^{2}= \int^{2e^{u}}_{e^{u}}u^{2}e^{u}du=[u^{2}e^{u}]^{2e^{u}}_{e^{u}}-\int^{2e^{u}}_{e^{u}}2ue^{u}e^{u}du$$ \\
    $$= [u^{2}e^{u}]^{2e^{u}}_{e^{u}}- ([2ue^{u}]^{2e^{u}}_{e^{u}}- \int ^{2e^{u}}_{e^{u}}2e^{u}du=[u^{2}e^{u}] ^{2e^{u}}_{e^{u}}-[2ue^{u}-2e^{u}]^{2e^{u}}_{e^{u}}=[u^{2}e^{u}-2ue^{u}-2e^{u}]^{2e^{u}}_{e^{u}}$$ \\
    $$=[x(\ln |x|)^{2}-2x\ln|x|-2x]^{2x}_{x} \because u=\ln|x| \Rightarrow e^{u}=x $$ \\
    $\therefore I_2=x[2(\ln |2x|)^{2}-(\ln |x|)^{2}-\ln |16x^{2}|]$ (\text{This result $\rightarrow$ from evaluating the bounds}) \\
    $$I_1= \int^{(3+x)^{6}}_{I_{2}} (\frac{1}{3e^{x}\cos x \sec^{2} x} + \cot x \csc x) \ dx = \int^b_a(\frac{1}{3e^{x}\cos x \sec^{2} x)} + \int^{b}_{a} \cot x \csc x$$ \\
    $$let \ I_{3}= \int^b_a(\frac{1}{3e^{x}\cos x \sec^{2} x)} = \int^b_a(\frac{1}{3e^{x}\sec x)}dx = \frac{1}{3} \int^b_a(e^{-x}\cos x)dx$$ \\
    $$I_{3}=1/3(J) $$ \\
    $$J=[-e^{-x}\cos x]^b_a - \int^b_a -e^{-x}\sin x = [-e^{-x}\cos x]^b_a-([-e^{-x}\sin x]^b_a-\int^b_ae^{-x}cosx$$ \\
    $$J=[-e^{-x}\cos x]^b_a-[e^{-x}\sin x]^b_a-J $$ \\
    $$\therefore \ J=\frac{1}{2}[e^{-x}\sin x-e^{-x}\cos x]^b_a$$ \\
    $$\therefore \ I_{3}=\frac{1}{6}[e^{-x}\sin x-e^{-x}\cos x]^b_a$$ \\
    $$I_{1}=I_{3}+\int^b_a\cot x \csc x \ dx$$ \\
    $$ let \ I_{4}= \int^b_a\cot x \csc x \ dx$$ \\
    $$I_{4}= \int^b_a (\frac{1}{\sin x})(\frac{\cos x}{\sin x}) \ dx = \int^b_a \frac{\cos x}{1-\cos^{2} x} \ dx $$ \\
    \textbf{Integrate $I_4$ by parts:}
    $$ I_{4}=\int^b_a \frac{\cos x}{\sin^{2} x} \ dx$$ \\
    $$= \int^b_a \cos x ( \frac{1}{\sin^{2} x}) \ dx = [\frac{1}{\sin x}]^b_a-\int^b_a \sin x ( \frac{-2\sin x\cos x}{\sin^{4} x}) \ dx = [\frac{1}{\sin x}]^b_a-\int^b_a \frac{-2 \cos x}{\sin x} \ dx $$ \\
    $$ \therefore I_{4}= [\frac{1}{\sin x}]^b_a+ 2I_{4}$$ \\
    $$\Rightarrow I_{4}=-\frac{1}{\sin x} $$
    $$ \therefore I_{1}= [I_{3}+I_{4}]^b_a $$
    \footnote{ \textbf{ Warning:} Solution is unverified}
    $\therefore$ The integral $I_{1}$ can be written as a single expression within its bounds
    $\therefore$ Q.E.D

    \newpage
    \section{Euclidian Geometry}
    \subsection{\underline{Problem One:}}
    \textbf{IMO 2011}

Let $S$ be a finite set of at least two points in the plane. Assume that no three points of $S$ are collinear. A windmill is a process that starts with a line $\ell$ going through a single point $P \in S$. The line rotates clockwise aboutthe pivot $P$ until the first time that the line meets some other point belonging to S. This point, $Q$, takes over as the new pivot, and the line now rotates clockwise about $Q$, until it next meets a point of $S$. This process continues indefinitely. Show that we can choose a point $P$ in $S$ and a line $\ell$ going through $P$ such that the resulting windmill uses each point of $S$ as a pivot infinitely many times.

\textit{[12 Marks]} \\

\subsection {\underline{Problem Two:}}
\textbf{\emph{Problem Author: Zain Sikand}}
\newline \\  

Imagine Let \(T_{1}\) be a tetrahedron and let \(S_{1}\) be its circumsphere with radius \(R\).  
For each radius of \(S_{1}\), extend it to a full line and denote this line by \(\ell\).

In the plane \(z = 0\), consider a circle \(C_{1}\) which circumscribes an equilateral triangle whose sides are tangent to the coordinate axes \(x = 0\) and \(y = 0\).  Thus the triangle has one vertex at the origin and its other two vertices lie on the positive coordinate axes.

Suppose that for certain choices of the radius of \(S_{1}\), the corresponding line \(\ell\) intersects the plane \(z = 0\) and is tangent to the circle \(C_{1}\).  The set of all such tangent lines \(\ell\) is finite.

Determine, in terms of \(R\), the area of the circle \(C_{1}\).

\subsection{\underline{Problem Three:}}
\textbf{\emph{Problem Author: Carter Owen}} 
\newline \\ 
Figure 1.1 shows a right-angled triangle $\triangle ABC$ of height $H$, divided vertically by a straight line $\ell$ such that it meets the triangle at a point defined by the variable $\phi$. The division of $\triangle ABC$ splits it at $\phi$ into a trapezium $CD{\phi}A$ and a new right angled triangle $\triangle DB{\phi}$. Deduce the value(s) for $\phi$ that divides $\triangle ABC$ such that the area of $CD{\phi}A$ is equal to that of $DB{\phi}$. 
\begin{center}
\begin{tikzpicture}[scale=1, font=\small]

  % Internal geometry (not printed)
  \def\b{7.2}        % base length (internal)
  \def\H{4.2}        % height (internal)
  \def\phival{2.6}   % internal numeric x-position of dividing line

  % Main triangle vertices
  \coordinate (A) at (0,0);
  \coordinate (B) at (\b,0);
  \coordinate (C) at (0,\H);

  % Intersection of the vertical line with the hypotenuse = D
  \coordinate (D) at (\phival, { \H*(1 - \phival/\b)});
  % Intersection with the base (labelled phi)
  \coordinate (P) at (\phival,0);

  % a little extra height for the dotted extension above the triangle
  \coordinate (Top) at (\phival, { \H + 0.9 });

  % Draw the triangle outlines
  \draw[line width=0.9pt] (A) -- (B) -- (C) -- cycle;

  % small right-angle box at A
  \draw[line width=0.8pt] ($(A)+(0.18,0)$) -- ++(0,0.18) -- ++(-0.18,0);

  % Solid segment INSIDE the triangle: from D down to base point P
  \draw[line width=0.9pt] (D) -- (P);

  % Dotted extension ABOVE the triangle: from Top down to D (dotted)
  % label \ell near the dotted part above D
  \draw[dotted, line width=0.9pt] (Top) -- (D) node[pos=0.14, right=2pt, yshift=4pt] {$\ell$};

  % re-draw region boundaries to ensure consistent stroke weights
  \draw[line width=0.7pt] (A) -- (P); % left base segment
  \draw[line width=0.7pt] (P) -- (B); % right base segment
  \draw[line width=0.7pt] (A) -- (C); % left vertical
  \draw[line width=0.7pt] (C) -- (D); % left part of hypotenuse
  \draw[line width=0.7pt] (D) -- (B); % right part of hypotenuse

  % Labels: A, B, C
  \node[below left]  at (A) {$A$};
  \node[below right] at (B) {$B$};
  \node[above] at (C) {$C$};

  % Label D at intersection (slightly above-left to avoid overlap)
  \node[above left, yshift=1pt] at (D) {$D$};

  % Label the base intersection as phi (symbol only)
  \node[below] at (P) {$\phi$};

\end{tikzpicture}
\end{center}
\captionof{figure}{}
\subsection{\underline{Problem Four:}}
\textbf{\emph{Moscow State University, 1989}} \\
In a Trapezium KLMN, sides $KN$ and $LM$ are paralell, with $KN=3$ and $M= \angle 120^{\circ} $. $LM$ and $MN$ are tangent to the circle circumscribed about $\triangle KLN$. Find the area of $\triangle KLN$. \\
\textit{[6 Marks]} 
\newpage
\section{Real Analysis}
\subsection{\underline{Problem One:}} 
\textbf{\emph{IMO 2022}}
\newline \\ 
Let $\mathbb{R^{+}}$ denote the set of positive real numbers. Find all functions $f : \mathbb{R}^{+} \rightarrow \mathbb{R}^{+}$ such
that for each $x \in \mathbb{R^{+}}$, there is exactly one $y \in \mathbb{R^{+}}$ satisfying $$ xf(y)+yf(x) \leq 2$$

\chapter{Physics}
\textit{\emph{Definition:} Physics,} \textbf{The study of all things that exist to place one under  mental, spiritual, and physical duress}
\newpage
\section{Kinematics and Further Mechanics}
\subsection{\underline{Problem One:}}
\textbf{\emph{Problem Author: Zain Sikand}} 
\newline \\
A person moving at speed $S$ whistles, stopping once after 5 seconds of walking. $t=15s$ later, he continues walking along his current trajectory before passing a stationary group of people. The group of people begin to hear the whistling at $t=30s$ before he passes them. Determine the speed at which the man is walking, assuming the \textbf{speed of sound= $330ms^{-1}$}

\subsection{\underline{Problem Two:}}
\textbf{\emph{BAAO 2022-23}} 
\newline \\ 
The very first image released by the JamesWebb Space Telescope (JWST) was of a galaxy cluster
called SMACS 0723. The image is considered to be Webb’s first deep field, since a long exposure
time of 12.5 hours was used to allow the light from very faint and distant galaxies to be seen. The
spectrum of one such galaxy is shown in Figure 2.1. 
\newline \\ 
|Insert Figure Here| 

The spectrum shows four bright hydrogen lines, which are part of the Balmer series (some of
which are normally seen in the visible). The rest frame wavelengths of the longest four lines in
the series are 410 nm, 434 nm, 486 nm and 656 nm \textbf{(not all of which are visible in the spectrum)}.
Once a redshift is known, its recessional velocity can be calculated. At very high redshifts, such
as these, General Relativity must be used. A conversion from redshift to recessional velocity is
shown in Figure 3. 
\newline \\ 

a) Taking measurements from the spectrum, estimate the redshift of the galaxy. [Hint: you
should measure more than one line to ensure you correctly identify which rest frame
wavelength corresponds to which line.] \\ 
b) Taking the value of the Hubble constant to be $H_{0} = 70kms^{-1}Mpc^{-1}$, what is the distance
to the galaxy? Give your answer in Mpc. \\ 

\end{raggedright}
\end{document}